The Perils of Exploration under Competition: \\ A Computational Modeling Approach

### 2020-09-24 journal paper/content/sim_details.tex
add bergemann valimaki paper comparisons
a pass through related work and remaining color edits
fix broken links

\xhdr{Challenges.} An ``atomic experiment" is a competition game between a given pair of bandit algorithms, in a given competition model, on a given instance of a multi-armed bandit problem (and each such experiment is run many times to reduce variance). Accordingly, we have a three-dimensional space of atomic experiments one needs to run and interpret: \{pairs of algorithms\} x \{competition models\} x \{bandit instances\}, and we are looking for findings that are consistent across this entire space. It is essential to keep each of the three dimensions small yet representative. In particular, we need to capture a huge variety of bandit algorithms and bandit instances with only a few representative examples. Further, we need a succinct and informative summarization of results within one atomic experiment and across multiple experiments (\eg see Table~\ref{sim_table}).
\asmargincomment{copied from intro}

@@

\xhdr{MAB algorithms.} In abstract terms, we posit three types of technology, from ``low" to ``medium" to ``high". Concretely, we consider three essential classes of bandit algorithms: ones that never explicitly explore (\emph{greedy algorithms}), ones that explore without looking at the data (\emph{exploration-separating algorithms}), and ones where exploration gradually zooms in on the best arm (\emph{adaptive-exploration algorithms}). In the absence of competition, these classes are fairly well-understood: greedy algorithms are terrible for a wide variety of problem instances, exploration-separated algorithms learn at a reasonable but mediocre rate across all problem instances, and adaptive-exploration algorithms are optimal in the worst case, and exponentially improve for ``easy" problem instances (see Appendix~\ref{app:bg} for more details).
\asmargincomment{copied from CODE submission}

@@

\xhdr{Running time.}
The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 2.2 GHz CPU cores, with 8 GB RAM per core. Each experiment took about $10$ hours.

>>>>

\xhdr{Challenges.} An ``atomic experiment" is a competition game between a given pair of bandit algorithms, in a given competition model, on a given instance of a multi-armed bandit problem (and each such experiment is run many times to reduce variance). Accordingly, we have a three-dimensional space of atomic experiments one needs to run and interpret: \{pairs of algorithms\} x \{competition models\} x \{bandit instances\}, and we are looking for findings that are consistent across this entire space. It is essential to keep each of the three dimensions small yet representative. In particular, we need to capture a huge variety of bandit algorithms and bandit instances with only a few representative examples. Further, we need a succinct and informative summarization of results within one atomic experiment and across multiple experiments (\eg see Table~\ref{fig:market_share}).

@@

\xhdr{MAB algorithms.} In abstract terms, we posit three types of technology, from ``low" to ``medium" to ``high". Concretely, we consider three essential classes of bandit algorithms: ones that never explicitly explore (\emph{greedy algorithms}), ones that explore without looking at the data (\emph{exploration-separating algorithms}), and ones where exploration gradually zooms in on the best arm (\emph{adaptive-exploration algorithms}). In the absence of competition, these classes are fairly well-understood: greedy algorithms are terrible for a wide variety of problem instances, exploration-separated algorithms learn at a reasonable but mediocre rate across all problem instances, and adaptive-exploration algorithms are optimal in the worst case, and exponentially improve for ``easy" problem instances (see Appendix~\ref{app:bg} for more details).

@@

\OMIT{
\xhdr{Running time.}
The simulations are computationally intensive. An experiment on a particular MAB instance comprised multiple runs of the competition game: $N$ mean reward vectors times $9$ pairs of algorithms times three values for the warm start. We used a parallel implementation over a cluster of 12 2.2 GHz CPU cores, with 8 GB RAM per core. Each experiment took about $10$ hours.
}

### 2020-09-24 journal paper/ec19paper/content/revisited.tex
fix broken links

However, we find a more nuanced picture. For example, in Figure \ref{sim_table} we see that $\DynamicGreedy$ attains a larger market share than $\DynamicEpsGreedy$ even for large warm starts. We find that this also holds for $K = 3$ arms and longer time horizons, see the supplement for more details. We conclude \asedit{that Conjecture~\ref{conj:mean-trajectories} is false:}

>>>>

However, we find a more nuanced picture. For example, in Figure \ref{fig:market_share} we see that $\DynamicGreedy$ attains a larger market share than $\DynamicEpsGreedy$ even for large warm starts. We find that this also holds for $K = 3$ arms and longer time horizons, see the supplement for more details. We conclude \asedit{that Conjecture~\ref{conj:mean-trajectories} is false:}
